% !TEX root = ../my-thesis.tex
%
\chapter{On Level Sets Preservation}
\label{sec:appendix}

From Eqs. (\ref{es121})-(\ref{es124}) and using a change of coordinated from Cartesian to Polar

\begin{equation}
    x_{1}=r_{1}\cos{\theta_{1}}\text{, } \hspace{0.5cm} y_{1}=r_{1}\sin{\theta_{1}} \text{, } \hspace{0.5cm} x_{2}=r_{2}\cos{\theta_{2}} \hspace{0.5cm} \text{ and} \hspace{0.5cm} y_{2}=r_{2}\sin{\theta_{2}}
\end{equation}

the two-cell network is described by the following set of equations

\begin{equation}
    \frac{dr_{1}}{dt} = r_{1}\lambda_{1} - r_{1}^{3}b_{1} + \cos{\theta_{1}}\left(\alpha_{11}r_{1}\cos{\theta_{1}} + \alpha_{12}r_{2}\cos(\theta_{2})\right)
\end{equation}
\begin{equation}
  \frac{d\theta_{1}}{dt} = \omega_{1}+a_{1}r_{1}^{2} -\sin{\theta_{1}}\left( \alpha_{11}r_{1}\cos{\theta_{1}} + \alpha_{12}r_{2}\cos{\theta_{2}} \right)
\end{equation}

\begin{equation}
    \frac{dr_{2}}{dt} = r_{2}\lambda_{2} - r_{2}^{3}b_{2} + \cos{\theta_{2}}\left(\alpha_{21}r_{1}\cos{\theta_{1}} + \alpha_{22}r_{2}\cos(\theta_{2})\right)
\end{equation}
\begin{equation}
  \frac{d\theta_{2}}{dt} = \omega_{2}+a_{2}r_{2}^{2} -\sin{\theta_{2}}\left( \alpha_{21}r_{1}\cos{\theta_{1}} + \alpha_{22}r_{2}\cos{\theta_{2}} \right)
\end{equation}

If individual level sets are preserved, then each individual oscillators presents a limit circle with values $\bar{r_{1}} = \sqrt{\lambda_{1}/b_{1}}$ and $\bar{r_{2}} = \sqrt{\lambda_{2}/b_{2}}$. Necessary and sufficient conditions for the existence of each limit circle are

\begin{equation}
    \alpha_{11}\bar{r_{1}}\cos{\theta_{1}} + \alpha_{12}\bar{r_{2}}\cos(\theta_{2}) = 0
    \label{A1}
\end{equation}
\begin{equation}
    \alpha_{21}\bar{r_{1}}\cos{\theta_{1}} + \alpha_{22}\bar{r_{2}}\cos{\theta_{2}} = 0
    \label{A2}
\end{equation}

We note that Eqs. (\ref{A1})-(\ref{A2}) not only do guarantee the existence of a limit circle in each cell, but also the preservation of the individual cell frequency. From Eqs. (\ref{A1})-(\ref{A2}) a necessary condition for the existence of a limit circle in each cell can be obtained.

\begin{Statement}
A necessary condition for the existence a limit circle in each cell in the two-cell linear network is that the connectivity matrix has to be singular. Therefore,
\begin{equation}
    \alpha_{11}\alpha_{22} = \alpha_{21}\alpha_{12} \Longrightarrow \frac{\alpha_{11}}{\alpha_{12}} = \frac{\alpha_{21}}{\alpha_{22}} 
    \label{A3}
\end{equation}
\end{Statement}

Taking into account Eq. (\ref{A3}), and Eqs. (\ref{A1})-(\ref{A2}) one condition is obtained for the existence of a individual limit circle in each cell

\begin{equation}
    r_{1}\cos{\theta_{1}} = - \Gamma r_{2}\cos{\theta_{2}}
    \label{A4}
\end{equation}

being 

\begin{equation}
\Gamma = \frac{\alpha_{12}}{\alpha_{11}} = \frac{\alpha_{22}}{\alpha_{21}}
\end{equation}

Two set of solutions are found to Eq. (\ref{A4}) which involve amplitude and phase difference ($\Delta \varphi$) relations between cells.

\begin{enumerate}
    \item The first solution corresponds to two oscillators in phase
    \begin{equation}
        \Gamma = \frac{r_{1}}{r_{2}} \hspace{0.5cm}  \text{and} \hspace{0.5cm} \theta_{1} = \theta_{2} \hspace{0.2cm} (\Delta \varphi = 0)
         \label{A5}
    \end{equation}
    \item The second solution corresponds to two oscillators out of phase (antiphase)
        \begin{equation}
        \Gamma = -\frac{r_{1}}{r_{2}} \hspace{0.5cm} \text{and} \hspace{0.5cm} \theta_{1} = \theta_{2} \pm \pi \hspace{0.2cm} (\Delta \varphi = \pm \pi)
         \label{A6}
    \end{equation}
\end{enumerate}

The previous two set of solutions are the only two possible solutions for the existence of a (intrinsic) limit circle in each cell in the two-cell network.

Computationally, conditions for the existence of a stable limit circle in each cell can be obtained. More specifically, the subspace on the connectivity parameter space (the $\alpha_{12}-\alpha_{21}$ parameter space) for which there exist a stable limit circle in each cell can be obtained. Within this subspace, Eqs. (\ref{A5})-(\ref{A6}) represent solutions that preserve individual LSs in the two-cell network.

